Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added some conclusions.

\section{Conclusion}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

>>>>

\section{Conclusion}
It is clear that our original hypotheses were not supported by our results.  That
is, we were not able to see consistent, significant speedup from any of our load
balancing schemes.  In many scenarios, the GPU simply outperformed the CPU, with
the static load balancing schemes falling somewhere between the two, and the dynamic
load balancer being far worse than anything else.  There were only two notable
exceptions to this trend.  The first was the reduction benchmark on the discrete GPU
platform, where the CPU outperformed the GPU due to the low stream processor utilization
inherent in a GPU reduction implementation.  However, the static load balancing schemes
were still outperformed by the CPU in this case, so no overall speedup was gained. The
second exception was the vector add+ benchmark on the discrete GPU platform, where the
dynamic load balancer actually outperformed the tested static load balancing schemes.
However, this was due to the vast disparity in the GPU and CPU runtimes for this
particular benchmark; giving any significant amount of data to the CPU would hurt
performance.  With the dynamic load balancer, the CPU will only compute a few blocks
of data, rather than 25\% or more with the static load balancer.

When analyzing more finely-grained static execution ratios, we found that, in the case
where the GPU outperforms the CPU, there is always a downward trend in overall runtime
as more data is executed on the GPU.  There were a couple sparse instances where a static
execution ratio performed better than using just the GPU, but we chalked these up to
typical variability in runtimes due to their infrequency and minute performance improvements.

When analyzing the results, we considered the possibility that the CPU and GPU kernels were
actually running in serial, which would explain the performance trends we were seeing in our
static and dynamic load balancing schemes.  An AMD profiler was used to find out the times each
kernel took to compute, and the sum of these times was compared to the actual runtime of the
benchmark.  We found that the actual runtime of the benchmark was typically slightly more than
the sum of the runtimes of each kernel, which seemed to indicate that the kernels were indeed
running serially, with some overhead for data transfer times.

Based on the CPU-only and GPU-only runtimes of each benchmark, we were able to calculate an
optimal static data partitioning, such that the computations on the CPU and GPU took equal
time to complete.  Based on the disparity of runtimes between the CPU-only and GPU-only
results, the optimal runtimes ranged from a 2\% to nearly a 45\% speedup over just the GPU
alone.  Unfortunately,
